\subsection{Scenarios}
\subsubsection{Scenario 1}
Mario is the CEO of a manufacturing company in Milan, his company collaborates with many shops located throughout in the region. Once a month he musts to visit each shop for get a report of administrative and management activities. To organize and take into account the travel time from the appointments, he uses Travlendar+. After downloaded the application and registered his data, Mario has the possibility to create a meeting into the app for every appointment that he has in his personal calendar. During the meeting creation, he needs to specify the following information: location for the meeting, starting and ending time, name and type of the appointment. The app calculate in autonomous way if the travel time between two meetings is enough respect the ending time of the first meeting and the starting time of the second one, if it is not a warning dialog is shown to the user.

\subsubsection{Scenario 2}
Luca is a young architect of Milan, and in addition to using the latest graphic system to realize his project, he usually produces a demonstration model for his customers scattered around the city. The great capabilities of Luca permits to him to have a lot of appointments, so he use Travlendar+ for manage the events. Luca has also set the preferences to use car sharing systems for work appointments, in this way he can carry his models around the town without risks of broken theirs. The preferences system implemented in the application shows  to the user the itineraries to the meeting’s location ordered by the preferences type selected for the meeting.

\subsubsection{Scenario 3}
Travlendar+ is the perfect application for Giovanni, father of family and financial advisor.
With the application Giovanni can easy manage his travel time to reach every type of appointment. Travlendar+ always suggests to him the perfect way to reach a meeting, in case of work’s meeting the primary suggestion is public transportation, instead in case of family’s meeting the primary suggestion is his own car. When Giovanni chooses the public transportations for his movement he can also buy the ticket directly on the app, in a simple way he can select the payment system and in a few tap he receives the ticket on his email. Furthermore in case of strike the app send a notification alert to the user and it will recalculate the travel based on the new options.

\subsubsection{Scenario 4}
Antonio is an event organizer and meantime he is a food’s lover; this is the reason why in his calendar is always presents a lunch in one of the best restaurant of Milan. Antonio is a daily user of Travlendar+ for this reason, the app in fact force a mandatory break of at least 30 minutes for lunch. Antonio can set the length of his lunch break in a period of time between the 11.30 am and the 2.30 pm. He must set the location where he wants to eat in such way that he can arrive in time for the next appointment. Over the lunch break, Antonio usually plans a break in the afternoon, with Travlendar+ he can do this and the minimum time for the break is 5 minutes

\subsubsection{Scenario 5}
Alex is a olympic championship of foot race, when he doesn’t do the train he often invited in some sport conferences. Alex always suggests that is most important doing physical activity not only during the training sessions but also when we choose the way for moving around the city. For this reason Alex can not do to use Travlendar+, indeed he chooses the bicycle for his movement and also select the option for minimize the carbon footprint. Furthermore the application notify Alex when the weather condition is not optimal and suggest to him to use another travel means for reach the desiderated location.
