This chapter presents some of algorithms of the application; their code is written in a Java-like pseudocode.


\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
 
\lstset{style=mystyle}

\subsection{Is Overlapped}
This algorithm is used during the process of creation of a meeting and checks wether the new meeting that the user wants to create would be overlapped with another already scheduled.
In case of overlaps, the method returns true.
\lstinputlisting[language=java]{Code/isOverlapped.java}

\subsection{Create Meeting}
This algorithm is used during the process of creation of a meeting and checks if, given an already scheduled meeting and given the computed journey to reach the second one, the second meeting is reachable or not.
In case the second meeting is unreachable, the method returns true.

\lstinputlisting[language=java]{Code/nextUnreachable.java}

\subsection{Check User Preferences}
This algorithm is used to check if the new setting selected by the user would create a conflict with an already planned (future) meeting.
If any of the preferences would create a conflict, the method returns false.

\lstinputlisting[language=java]{Code/checkPreferences.java}

\subsection{Find Best Journey}
This algorithm is used to filter the journeys list to find the best one for the user.
The function takes in consideration all the constraints depending on the journey length, on the weather and on the meeting.
Then, all the journeys are ordered according to a criterion (footprint, duration), eventually the best journey that also respect the "prefered travel mean for the meeting type" preference is selected and returned.

\lstinputlisting[language=java]{Code/findBestJourney.java}
