The project will be developed with a bottom-up approach, in this way the system can be divided in groups of components that can be developed independently. 
Furthermore the testing phase will be done in parallel with the implementation.
The development of the server and of the mobile applications will proceed in parallel.
The most critical part for both the client and the server is the model, which is the first component that will be developed.
Then, the development of the application will move on all the standalone components that do not need the connection to the server to work.
In this way we will obtain a fully functional application, that could work without a server and without user’s account and backup functions.
Particular attention will be given to the testing of all the functions, in particular we will focus on the functions that require an internet connection and a GPS system.
Navigation simulation will be performed to test the navigation system and its reliability.
Intensive tests will be performed to check if the Event Manager complies with all the functional requirements of the application.
Other tests will be performed to check if the non-functional requirements are satisfied.
Instead, the development of the server, after the implementation of its model will move to the implementation of the connection part, so that it could be fully functional before the implementation of the account and backup functions in the clients.
Tests will concentrate on the security and reliability aspect; the security of the system will be tested to check if there are vulnerabilities that could compromise the user data, while reliability will be tested together with durability.
The reliability of the system will be tested to assure that the requirements are respected, whereas durability test will ensure that in case of problems the user data wouldn’t be subject to losses or damages.
Once the network part of the server is completed and once the server is fully functional, we will proceed with the development of the components of the mobile applications that require a server.
These parts will be the last to be developed and, given the fact that most of these depend on the server, the effort in testing them won’t be minimal respect to the one spent for the other components.
When all the part will be completed and the system will be deployed, we will continue performing test and checks to guarantee the efficiency and reliability of the system and to avoid possible problems introduced by mobile systems updates.
