All the decisions in the DD have been taken following functional and nonfunctional requirements written in the RASD. In this chapter, each requirement is mapped to specific component.
\\
\begin{itemize}

\item
\textbf{LoginManager:}
\begin{itemize}
\item
$[$R.G.1$]$ An account requires an username.
\item
$[$R.G.2$]$ An account requires an email address.
\item 
$[$R.G.3$]$ An account requires a password.
\item
$[$R.G.4$]$ The email address must be unique.
\item
$[$R.G.5$]$ The user must be logged in the application.
\end{itemize}

\item
\textbf{EventManager:}
\begin{itemize}
\item
$[$R.1.1$]$ A meeting requires a location, which is either coordinates or an address.
\item
$[$R.1.2$]$ A meeting requires a starting and ending hour.
\item
$[$R.1.3$]$ A meeting requires a name.
\item
$[$R.1.4$]$ A meeting requires a type.
\item
$[$R.1.5$]$ A meeting may have a description.
\item
$[$R.2.1$]$ A warning should be given at the creation of a meeting if it is unreachable or if
it is causes conflicts.
\item
$[$R.2.2$]$ A warning should be given in case of exceptional events that make one or more
meetings unreachable.
\item
$[$R.2.3$]$ A warning forbids the user to force the creation of a meeting.
\item
$[$R.5.1$]$ The minimum length of a lunch break is 30 minutes.
\item
$[$R.5.2$]$ The lunch break must be scheduled between 11.30 am and 2.30pm.
\item
$[$R.6.1$]$ The minimum length of a lunch break is 5 minutes.
\end{itemize}

\item
\textbf{Configurator:}
\begin{itemize}
\item
$[$R.3.2$]$ Different type of meetings should be reached with different/specific travel means.
\item
$[$R.3.3$]$ Different travel means should be suggested depending on the hour of the day.
\item
$[$R.3.4$]$ Travel means can have constraints on the length of their journey section.
\item
$[$R.4.1$]$ The application must support different travel means and transportation systems.
\item
$[$R.4.2$]$ Users can select constraints on travel means.
\item
$[$R.4.3$]$ The application must show results consistent with the users preferences.
\item
$[$R.4.4$]$ Users should be able to specify the travel passes they own.
\item
$[$R.4.5$]$ Users must specify their home address.
\item
$[$R.4.6$]$ Users can disable travel means.
\item
$[$R.4.7$]$ Users can enable the option to minimize air pollution.
\item
$[$R.6.2$]$ Users can set as many breaks as they want.
\item
$[$R.6.3$]$ Users can select the time slot in which they want their break to be scheduled.
\end{itemize}

\item
\textbf{JourneyManager:}
\begin{itemize}
\item
$[$R.3.1$]$ Different travel means should be suggested depending on the weather conditions.
\item
$[$R.3.3$]$ Different travel means should be suggested depending on the hour of the day.
\item
$[$R.7.1$]$ The application should notify the user when he has to get off from a transportation system.
\item
$[$R.7.2$]$ The applications should give directions to the users when they are driving, cycling or walking.
\end{itemize}

\item
\textbf{PaymentHandler:}
\begin{itemize}
\item
$[$R.7.3$]$ Users can buy travel passes through the application.
\end{itemize}

\item
\textbf{SharedController:}
\begin{itemize}
\item
$[$R.7.4$]$ The application must locate the nearest vehicle of the selected sharing system.
\end{itemize}
\end{itemize}